How and Why to run a Hack Week

### 2017-08-17 sections/design.tex
Use the correct citation format. Replace all "citep" => "cite"
Bingo!

The \textit{impostor phenomenon}, or \textit{impostor syndrome} (IS) is a dissonant feeling experienced by certain high-achieving individuals, that despite objective evidence to the contrary, they are in fact not as intelligent or capable as they appear.
Individuals with IS thus experience a fear of being ''found out``, shamed and expelled from their environment \citep{Clance1978-ef}.
Initial observations of the first Astro Hack Week conducted by data science ethnographer Brittany Fiore-Gartland\footnote{\url{http://astrohack week.org/blog/ethnographic-notes.html}} suggested that hack weeks are an environment prone to a particular kind of IS: participants might feel the need to be experts in multiple aspects of the activities pursued during a hack week: expertise in a scientific domain, as well as expertise in a the variety of technical tools used.
This particular form of IS hinges to some degree on the design focus on diversity of backgrounds (everyone else seems to know something that you do not!) and might be further exacerbated by the expectation that attendants expose their ideas to public scrutiny, find collaborators in a very short amount of time, and not least produce and present a successful hack at the end of the week\footnote{see also this insightful blog post: \url{https://medium.com/astronomy-without-stars/the-horror-of-hack-days-52c6b52cfc3b}}.
The prevalence of IS at a hack week may be endemic to the format, and should thus be a major concern for any organizing committee.
This is because of the chilling effect it tends to have on participants and the community as a whole, and particularly on women (in particular in fields in which women are under-represented) and members of ethnic and racial minorities, correlating with anxiety and other forms of mental distress \citep{Parkman2016-ro}.
Less severely, another major concern is that IS inhibits risk taking: participants experiencing it will be less likely to ask a question, to put forward an idea for a hack, to be pro-active about forming new collaborations.
 Many of the goals of a hack week, including the successful completion of projects, lateral knowledge transfer, as well as community building are hampered.
We are working within our hack weeks to mitigate IS using various techniques.
With respect to minority participants, ensuring adequate representation can decrease feelings of otherness and may help reduce IS.
More generally, being open about the presence and prevalence of IS can help participants feel more at ease.%(e.g. one Astro Hack Week participant remarked in a survey, \textit{''I really appreciated the direct acknowledgement of impostor syndrome on the first day.
%I think it helped ease the feeling!!``}).
Additionally, role models are very effective at encouraging positive behaviour: asking participants with prior experience at hack weeks at all academic levels to ask questions, even when they might know the answer, can help foster an inclusive environment that rewards risk taking.

>>>>

The \textit{impostor phenomenon}, or \textit{impostor syndrome} (IS) is a dissonant feeling experienced by certain high-achieving individuals, that despite objective evidence to the contrary, they are in fact not as intelligent or capable as they appear.
Individuals with IS thus experience a fear of being ''found out``, shamed and expelled from their environment \cite{Clance1978-ef}.
Initial observations of the first Astro Hack Week conducted by data science ethnographer Brittany Fiore-Gartland\footnote{\url{http://astrohack week.org/blog/ethnographic-notes.html}} suggested that hack weeks are an environment prone to a particular kind of IS: participants might feel the need to be experts in multiple aspects of the activities pursued during a hack week: expertise in a scientific domain, as well as expertise in a the variety of technical tools used.
This particular form of IS hinges to some degree on the design focus on diversity of backgrounds (everyone else seems to know something that you do not!) and might be further exacerbated by the expectation that attendants expose their ideas to public scrutiny, find collaborators in a very short amount of time, and not least produce and present a successful hack at the end of the week\footnote{see also this insightful blog post: \url{https://medium.com/astronomy-without-stars/the-horror-of-hack-days-52c6b52cfc3b}}.
The prevalence of IS at a hack week may be endemic to the format, and should thus be a major concern for any organizing committee.
This is because of the chilling effect it tends to have on participants and the community as a whole, and particularly on women (in particular in fields in which women are under-represented) and members of ethnic and racial minorities, correlating with anxiety and other forms of mental distress \cite{Parkman2016-ro}.
Less severely, another major concern is that IS inhibits risk taking: participants experiencing it will be less likely to ask a question, to put forward an idea for a hack, to be pro-active about forming new collaborations.
 Many of the goals of a hack week, including the successful completion of projects, lateral knowledge transfer, as well as community building are hampered.
We are working within our hack weeks to mitigate IS using various techniques.
With respect to minority participants, ensuring adequate representation can decrease feelings of otherness and may help reduce IS.
More generally, being open about the presence and prevalence of IS can help participants feel more at ease.%(e.g. one Astro Hack Week participant remarked in a survey, \textit{''I really appreciated the direct acknowledgement of impostor syndrome on the first day.
%I think it helped ease the feeling!!``}).
Additionally, role models are very effective at encouraging positive behaviour: asking participants with prior experience at hack weeks at all academic levels to ask questions, even when they might know the answer, can help foster an inclusive environment that rewards risk taking.

### 2017-08-17 sections/why.tex
Use the correct citation format. Replace all "citep" => "cite"
Bingo!

\begin{itemize}
\item{\textit{Education and training}: %Some hack weeks are more focused on education than others (see Figure 1).
Even those hackathons not explicitly focused on skills-development will include extensive discussions on reproducible and open science practices that are valuable to participants.
%Discussing these topics in a diverse group setting helps to ingrain within participants the basic conventions of the broader open source community.
Participants can then serve as ''ambassadors`` of these practices and foster their adoption by other researchers in the field.
Furthermore, the kind of co-working that is inherent to the hack week format facilitates lateral knowledge transfer, where participants learn from each other about practices and tools of the trade.}
%Often these tools are not described in research products such as papers, or even in the software implementations.}
\item{\textit{Tool development}: hack weeks present an opportunity for computational tool developers to get together with users of these tools, and to critically evaluate the use of the tools in addressing particular scientific questions.}
\item{\textit{Community building}: a hack week is an opportunity to galvanize a community within a field.% that cares about computational issues, and relates to specific open-source software projects.
For example, because of its focus on free and open-source tools, Neurohack week helps galvanize the Neuroimaging in Python (http://nipy.org) community.
It also allows researchers who may otherwise be isolated within their departments and subfield on account of their computational specialization to come together and exchange experiences.}
%As one participant at Astro Hack Week expressed in the survey, \textit{''The main thing I took from Astrohack week is the fact that I'm not alone``}.}
\item{\textit{Interdisciplinary research}: a short time-bounded event is an excellent opportunity to experiment with concepts, questions and methods that traverse boundaries within a discipline (e.g.\ between researchers using different methods, or studying different systems, or experimental models), as well as across disciplines.
Despite the impact of interdisciplinary research \citep{Hall2012-hi}, these experiments are often discouraged in traditional disciplinary research, because of the difficulty to achieve results in both disciplines, and because of the risks inherent in taking a less trodden path\footnote{\url{https://www.ncbi.nlm.nih.gov/labs/articles/12970550} and \url{https://www.researchgate.net/publication/8126355_EDUCATION_Risks_and_Rewards_of_an_Interdisciplinary_Research_Path}}.}
%This is despite the fact that interdisciplinary research can also be very impactful \citep{Hall2012-hi}.
%A diversity of research backgrounds, and interactions with scientists from other disciplines, further facilitates these experiments.}

>>>>

\begin{itemize}
\item{\textit{Education and training}: %Some hack weeks are more focused on education than others (see Figure 1).
Even those hackathons not explicitly focused on skills-development will include extensive discussions on reproducible and open science practices that are valuable to participants.
%Discussing these topics in a diverse group setting helps to ingrain within participants the basic conventions of the broader open source community.
Participants can then serve as ''ambassadors`` of these practices and foster their adoption by other researchers in the field.
Furthermore, the kind of co-working that is inherent to the hack week format facilitates lateral knowledge transfer, where participants learn from each other about practices and tools of the trade.}
%Often these tools are not described in research products such as papers, or even in the software implementations.}
\item{\textit{Tool development}: hack weeks present an opportunity for computational tool developers to get together with users of these tools, and to critically evaluate the use of the tools in addressing particular scientific questions.}
\item{\textit{Community building}: a hack week is an opportunity to galvanize a community within a field.% that cares about computational issues, and relates to specific open-source software projects.
For example, because of its focus on free and open-source tools, Neurohack week helps galvanize the Neuroimaging in Python (http://nipy.org) community.
It also allows researchers who may otherwise be isolated within their departments and subfield on account of their computational specialization to come together and exchange experiences.}
%As one participant at Astro Hack Week expressed in the survey, \textit{''The main thing I took from Astrohack week is the fact that I'm not alone``}.}
\item{\textit{Interdisciplinary research}: a short time-bounded event is an excellent opportunity to experiment with concepts, questions and methods that traverse boundaries within a discipline (e.g.\ between researchers using different methods, or studying different systems, or experimental models), as well as across disciplines.
Despite the impact of interdisciplinary research \cite{Hall2012-hi}, these experiments are often discouraged in traditional disciplinary research, because of the difficulty to achieve results in both disciplines, and because of the risks inherent in taking a less trodden path\footnote{\url{https://www.ncbi.nlm.nih.gov/labs/articles/12970550} and \url{https://www.researchgate.net/publication/8126355_EDUCATION_Risks_and_Rewards_of_an_Interdisciplinary_Research_Path}}.}
%This is despite the fact that interdisciplinary research can also be very impactful \cite{Hall2012-hi}.
%A diversity of research backgrounds, and interactions with scientists from other disciplines, further facilitates these experiments.}
